%%% Seznam použité latinratury je zpracován podle platných standardů. Povinnou citační
%%% normou pro~diplomovou práci je ISO 690. Jména časopisů lze uvádět zkráceně, ale jen
%%% v~kodifikované podobě. Všechny použité zdroje a prameny musí být řádně citovány.

\def\bibname{Seznam použité literatury}


\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}


\bibitem{flash}
  ADOBE. \textit{Adobe Flash Player} [software]. 2014.
  Dostupné z: \url{http://get.adobe.com/cz/flashplayer/}.

\bibitem{lucene}
  APACHE SOFTWARE FOUNDATION. \textit{Apache Lucene 4.9.0} [software]. 2014.
  Dostupné z: \url{http://lucene.apache.org/}.

\bibitem{apertium}
  APERTIUM. \textit{Apertium: A free/open-source machine translation platform} [software]. 2014.
  Dostupné z: \url{http://www.apertium.org/}.

\bibitem{wikiextractor}
  ATTARDI, Giuseppe. \textit{Wikipedia Extractor} [software]. 2013.
  Dostupné z: \url{http://medialab.di.unipi.it/wiki/Wikipedia_Extractor}.

\bibitem{elasticsearch-ruby}
  ELASTICSEARCH BV. \textit{elasticsearch-ruby} [software]. 2014.
  Dostupné z: \url{https://github.com/elasticsearch/elasticsearch-ruby}.

\bibitem{elasticsearch}
  ELASTICSEARCH BV. \textit{Elasticsearch 1.3.0} [software]. 2014.
  Dostupné z: \url{http://www.elasticsearch.org/}.

\bibitem{mufin}
  BATKO, Michal, et al. \textit{Mufin: A multi-feature indexing network}. In: Proceedings of the 2009 Second International Workshop on Similarity Search and Applications. IEEE Computer Society, 2009, 158-159.

\bibitem{botorek}
  BOTOREK, Jan. \textit{Tvorba nástroje pro~zpracování textových popisů multimediálních dat} [online]. 2012 [cit. 2014-07-17]. Bakalářská práce. Masarykova univerzita, Fakulta informatiky. Vedoucí práce Petra Budíková. Dostupné z: \url{http://is.muni.cz/th/359815/fi_b/}.

\bibitem{xml}
  BRAY, Tim, et al. \textit{Extensible markup language (XML)}. World Wide Web Consortium Recommendation REC-xml-19980210. http://www.w3.org/TR/1998/REC-xml-19980210, 1998.

\bibitem{brno}
  BUDÍKOVÁ, Petra, Michal BATKO a Pavel ZEZULA. \textit{Evaluation Platform for Content-based Image Retrieval Systems}. In International Conference on Theory and Practice of Digital Libraries 2011, LNCS 6966. Berlin: Springer, 2011, 130-142, ISBN~978-3-642-24468-1.

\bibitem{translation-demand}
  CASTELLANOS, Melissa. \textit{Interpreters and Translators Among Most In-Demand and High-Paying Jobs of 2014} [online]. 2014 [cit. 2014-07-17].
  Dostupné z: \url{http://bit.ly/1s6nvF9}.

\bibitem{cavnar}
  CAVNAR, William B., et al. \textit{N-gram-based text categorization}.
  In Proceedings of Third Annual Symposium on Document Analysis and Information Retrieval (SDAIR-94), 1994, 161-175.

\bibitem{chang}
  CHANG, Jonathan, et al. \textit{Reading tea leaves: How humans interpret topic models}. In: \textit{Advances in neural information processing systems}. 2009, 288-296.

\bibitem{couchbase}
  COUCHBASE. \textit{Couchbase 2.5.1} [software]. 2014.
  Dostupné z: \url{http://www.couchbase.com/}.

\bibitem{json}
  CROCKFORD, Douglas. \textit{The application/json media type for javascript object notation (json)}. 2006.
  Dostupné z: \url{http://tools.ietf.org/html/rfc4627.txt}.

\bibitem{mapreduce}
  DEAN, Jeffrey; GHEMAWAT, Sanjay. \textit{MapReduce: simplified data processing on large clusters}. Communications of the ACM, 2008, 51(1), 107-113.

\bibitem{ecmascript}
  ECMASCRIPT. \textit{ECMAScript Programming Language}. 2014.
  Dostupné z: \url{http://www.ecmascript.org/}.

\bibitem{websocket}
  FETTE, Ian; MELNIKOV, Alexey. \textit{The WebSocket Protocol}. 2011.
  Dostupné z: \url{http://tools.ietf.org/html/rfc6455}.

\bibitem{rest}
  FIELDING, Roy. \textit{Representational state transfer}. Architectural Styles and the Design of Netowork-based Software Architecture, 2000, 76-85.

\bibitem{golang-release}
  GERRARD, Andrew.
  \emph{Go version 1 is released} [online]. 2012 [cit. 2014-07-24].
  Dostupné z: \url{http://blog.golang.org/go-version-1-is-released}.

\bibitem{closure}
  GOOGLE INC. \textit{Closure Tools} [software]. 2014.
  Dostupné z: \url{https://developers.google.com/closure/}.

\bibitem{golang}
  GOOGLE INC. \textit{The Go Programming Language} [software]. 2014.
  Dostupné z: \url{http://golang.org/}.

\bibitem{googletranslate}
  GOOGLE INC. \textit{Překladač Google} [online]. 2014 [cit. 2014-07-25].
  Dostupné z: \url{http://tranlslate.google.cz}.

\bibitem{callback}
  HARTER, Mark. \textit{Managing Node.js Callback Hell with Promises, Generators and Other Approaches}. 2014.
  Dostupné z: \url{http://bit.ly/1uK01Ki}.

\bibitem{caffe}
  JIA, Yangqing. \textit{Caffe: An open source convolutional architecture for fast feature embedding}. 2013.
  Dostupné z: \url{http://caffe.berkeleyvision.org}.

\bibitem{tfidf}
  JONES, Karen Sparck. \textit{A statistical interpretation of term specificity and its application in retrieval}. Journal of documentation, 1972, 28(1), 11-21.

\bibitem{jquery}
  THE JQUERY FOUNDATION. \textit{jQuery} [software]. 2014.
  Dostupné z: \url{http://jquery.org/}.

\bibitem{koehn}
  KOEHN, Philipp. \textit{Statistical machine translation}. Cambridge University Press, 2009.

\bibitem{moses}
  KOEHN, Philipp, et al. \textit{Moses: Open source toolkit for statistical machine translation}. In: Proceedings of the 45th Annual Meeting of the ACL on Interactive Poster and Demonstration Sessions. Association for Computational Linguistics, 2007, 177-180.

\bibitem{websocket-study}
  LUBBERS, Peter; GRECO, Frank. \textit{HTML5 Web Sockets: A Quantum Leap in Scalability for the Web} [online].
  2013 [cit. 2014-07-25].
  Dostupné z: \url{http://www.websocket.org/quantum.html}.

\bibitem{lott}
  LOTT, Brian. \textit{Survey of Keyword Extraction Techniques}. UNM Education, 2012.

\bibitem{manning}
  MANNING, Christopher D.; RAGHAVAN, Prabhakar; SCHÜTZE, Hinrich. Introduction to information retrieval. Cambridge: Cambridge university press, 2008.

\bibitem{ruby}
  MATSUMOTO, Yukihiro, et al. \textit{Ruby Programming Language} [software]. 2014.
  Dostupné z: \url{https://www.ruby-lang.org/}.

\bibitem{silverlight}
  MICROSOFT. \textit{Microsoft Silverlight} [software]. 2014.
  Dostupné z: \url{http://www.microsoft.com/silverlight/}.


\bibitem{wordnet}
  MILLER, George A.
  \emph{WordNet: A Lexical Database for English}.
  Communications of the ACM, 1995, 38(11), 39-41.

\bibitem{porter80}
  PORTER, Martin F.
  \emph{An algorithm for suffix stripping}.
  Program: electronic library and information systems. MCB UP Ltd, 1980, 14(3), 130-137.

\bibitem{rails}
  RAILS CORE TEAM. \textit{Ruby on Rails} [software]. 2014 [cit. 2014-07-24].
  Dostupné z: \url{http://rubyonrails.org/}.

\bibitem{nosql}
  STRAUCH, Christof; SITES, Ultra-Large Scale; KRIHA, Walter. NoSQL databases. Lecture Notes, Stuttgart Media University, 2011.

\bibitem{geohash}
  WIKIPEDIA
  \emph{Geohash --- Wikipedia{,} The Free Encyclopedia} [online]. 2014 [cit. 2014-07-24].
  Dostupné z: \url{http://en.wikipedia.org/w/index.php?title=Geohash}.

\bibitem{mvc}
  WIKIPEDIA
  \emph{Model–view–controller --- Wikipedia{,} The Free Encyclopedia} [online]. 2014 [cit. 2014-07-28].
  Dostupné z: \url{https://en.wikipedia.org/w/index.php?title=MVC}.

\bibitem{wiki}
  WIKIPEDIA
  \emph{Wikipedia{,} The Free Encyclopedia} [online]. 2014 [cit. 2014-07-28].
  Dostupné z: \url{https://www.wikipedia.org}.

\bibitem{html5}
  THE WORLD WIDE WEB CONSORTIUM (W3C)
  \emph{HTML5} [online]. 2014 [cit. 2014-07-28].
  Dostupné z: \url{http://www.w3.org/TR/html5/}.

\bibitem{css3}
  THE WORLD WIDE WEB CONSORTIUM (W3C)
  \emph{CSS3} [online]. 2014 [cit. 2014-07-28].
  Dostupné z: \url{http://www.w3.org/Style/CSS/current-work}.

\bibitem{ecma}
  ZAYTSEV, Juriy. \textit{ECMAScript 5 compatibility table} [online]. 2014 [cit. 2014-07-28]
  Dostupné z: \url{http://kangax.github.io/compat-table/es5/}.


\end{thebibliography}

%\inputencoding{utf8}


